Scikit-learn: API design for machine learning

### 2013-06-20 paper.tex
wordings (3.1, 3.2)

Building on the core interface introduced in the previous section, we now
present in this section advanced API mechanisms for building meta-estimators,
composing complex estimators and then selecting models. We also discuss design
choices allowing for an easy use and extension of \sklearn.

@@

As an example, a logistic regression classifier
uses by default a one-vs.-rest scheme
for performing multiclass classification.
A different scheme can be achieved
by a meta-estimator wrapping a logistic regression estimator:
\begin{pythoncode}
ovo_lr = OneVsOneClassifier(LogisticRegression(penalty="l1"))
\end{pythoncode}
The \texttt{OneVsOneClassifier} object
\textit{clones} the LR estimator multiple times for learning,
resulting in a set of $\frac{K(K-1)}{2}$ estimator objects
for $K$-way classification,
all with the same settings,
that each perform a binary classification and vote to make the final decision.
The snippet exemplifies the importance
of separating object instantiation and actual learning.

Since using meta-estimators requires the construction of nested objects,
the decision to implement a meta-estimator
rather than fold the behavior it implements
into existing estimators classes
is always based on a trade-off between genericity and ease of use.
Relating to the example just given,
all \sklearn classifiers are designed to do multiclass classification
and the use of the \texttt{multiclass} module
is only necessary in advanced use cases.

@@

\texttt{FeatureUnion} combines multiple transformers
into a single one that concatenates their outputs.
I.e., a union of transformers that map inputs having $d$ features
to $d'$ and $d''$ features, respectively,
is a transformer that maps its $d$ input features to $d' + d''$ features
by calling its underlying transformers in parallel.
In terms of the API, a
\texttt{FeatureUnion} takes as input a list of transformers. Calling
\texttt{fit} on the union is the same as calling \texttt{fit} independently on
each of the transformers.

>>>>

Building on the core interface introduced in the previous section, we now
present advanced API mechanisms for building meta-estimators,
composing complex estimators and then selecting models. We also discuss design
choices allowing for an easy use and extension of \sklearn.

@@

As an example, a logistic regression classifier
uses by default a one-vs.-rest scheme
for performing multiclass classification.
A different scheme can be achieved
by a meta-estimator wrapping a logistic regression estimator:
\begin{pythoncode}
ovo_lr = OneVsOneClassifier(LogisticRegression(penalty="l1"))
\end{pythoncode}
For learning, the \texttt{OneVsOneClassifier} object
\textit{clones} the logistic regression estimator multiple times,
resulting in a set of $\frac{K(K-1)}{2}$ estimator objects
for $K$-way classification,
all with the same settings.
For predictions, all estimators perform a binary classification and then vote to make the final decision.
The snippet exemplifies the importance
of separating object instantiation and actual learning.

Since meta-estimators requires the construction of nested objects,
the decision to implement a meta-estimator
rather than fold the behavior it implements
into existing estimators classes
is always based on a trade-off between genericity and ease of use.
Relating to the example just given,
all \sklearn classifiers are designed to do multiclass classification
and the use of the \texttt{multiclass} module
is only necessary in advanced use cases.

@@

\texttt{FeatureUnion} objects combine multiple transformers into a single one
that concatenates their outputs. For example, a union of two transformers that
each maps inputs having $d$ features to $d'$ and $d''$ features respectively is
a transformer that maps its $d$ input features to $d' + d''$ features. In terms
of API, a \texttt{FeatureUnion} takes as input a list of transformers.
Calling \texttt{fit} on the union is the same as calling \texttt{fit}
independently on each of the transformers and then joining their outputs.
